\ProjectName{}: Data Imputation as a Query Optimization

### 2016-12-14 paper/queries.tex
paper: fix table generator & generate new tables

\begin{tabular}{ll}
\toprule
\# & Query \\
\midrule
0 & \verb|SELECT BLD FROM acs;| \label{q0} \\
1 & \verb|SELECT BLD as units_in_structure, COUNT(ST) as estimate FROM acs GROUP BY BLD;| \label{q1} \\
2 & \verb|SELECT BATH as has_bath, COUNT(ST) as ct FROM acs GROUP BY BATH;| \label{q2} \\
3 & \verb|SELECT ACR as lotsize, AVG(BDSP) as avg_num_bedrooms FROM acs GROUP BY ACR;| \label{q3} \\
4 & \verb|SELECT PSF as has_sub_families, SUM(NP) as num_people FROM acs GROUP BY PSF;| \label{q4} \\
5 & \verb|SELECT AVG(NP) as avg_num_people FROM acs;| \label{q5} \\
6 & \verb|SELECT BDSP as num_bedrooms, AVG(ACR) as avg_lot_size FROM acs WHERE VEH >= 2 GROUP BY BDSP;| \label{q6} \\
\bottomrule
\end{tabular}

>>>>

\newcounter{queryno}
\begin{tabular}{cl}
\toprule
\# & \multicolumn{1}{c}{Query} \\
\midrule
1 & \verb|SELECT BLD FROM acs;| \refstepcounter{queryno} \label{q1} \\
2 & \verb|SELECT BLD as units_in_structure, COUNT(ST) as estimate FROM acs GROUP BY BLD;| \refstepcounter{queryno} \label{q2} \\
3 & \verb|SELECT BATH as has_bath, COUNT(ST) as ct FROM acs GROUP BY BATH;| \refstepcounter{queryno} \label{q3} \\
4 & \verb|SELECT ACR as lotsize, AVG(BDSP) as avg_num_bedrooms FROM acs GROUP BY ACR;| \refstepcounter{queryno} \label{q4} \\
5 & \verb|SELECT PSF as has_sub_families, SUM(NP) as num_people FROM acs GROUP BY PSF;| \refstepcounter{queryno} \label{q5} \\
6 & \verb|SELECT AVG(NP) as avg_num_people FROM acs;| \refstepcounter{queryno} \label{q6} \\
7 & \verb|SELECT BDSP as num_bedrooms, AVG(ACR) as avg_lot_size FROM acs WHERE VEH >= 2 GROUP BY BDSP;| \refstepcounter{queryno} \label{q7} \\
8 & \verb|SELECT MIN(RMSP) as min_num_rooms FROM acs WHERE RWAT=2;| \refstepcounter{queryno} \label{q8} \\
9 & \verb|SELECT * FROM dirty m where m.f1 >= 2;| \refstepcounter{queryno} \label{q9} \\
10 & \verb|SELECT * FROM dirty where dirty.f1 <= 2;| \refstepcounter{queryno} \label{q10} \\
11 & \verb|SELECT MAX(f2) as max_f2 FROM dirty GROUP BY dirty.f1;| \refstepcounter{queryno} \label{q11} \\
12 & \verb|SELECT m1.f1, m1.f2 FROM dirty m1, clean m2 WHERE m1.f1 = m2.f1 and m1.f1 = 1 and m2.f2 = 69;| \refstepcounter{queryno} \label{q12} \\
13 & \verb|SELECT d1.f1 FROM dirty d1, clean d2 WHERE d1.f1 = d2.f1 and d2.f2 = 50;| \refstepcounter{queryno} \label{q13} \\
\bottomrule
\end{tabular}
